TacticToe: Learning the Game of Tactics

### 2018-01-29 tactictoe_jv.tex
minor

The exploration term is determined by the prior policy and the current policy 
where as the exploitation is exactly the current evaluation build from prior of 
evaluations of descendants of $a_i$.
\[Exploration(a_i) = \frac{PriorPolicy(a_i)}{CurPolicy(a_i)}\]

@@

The number $Failure(a_i)$ is the amount of failures that occurred during node 
extension from descendants of $a_i$ .
\end{definition}

>>>>

@@

The number $Failure(a_i)$ is the amount of failures that occurred during node 
extension from descendants of $a_i$ .

The exploration term is determined by the prior policy and the current policy.
\[Exploration(a_i) = \frac{PriorPolicy(a_i)}{CurPolicy(a_i)}\]

The coefficient $c_{exploration}$ is experimentally determined and adjusts the 
trade-off between exploitation and exploration.
\end{definition}
